Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-09 Docs/IJES/journal.tex
[A-6] In page 5, "Based on ..., (?) is called ..." (please, re-write the sentence).
[A-7] In page 5, "Three different optimization and decision problems", what are these problems? Is the problem addressed among these? why does you focus on that specific problem?

\vspace{2 mm}
Different optimization (and decision) problems can be defined, \cite{Arato2003}. In this paper, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related . Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as

>>>>

\vspace{2 mm}
In particular, different optimization (and decision) problems can be defined for partitioning HW-SW, as described by~\cite{Arato2003}. In this paper, however, the focus is on systems with hard real-time constraints: $ S_0 $ is given (initial cost of software), {\it i.e.}, the goal is to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related. Consequently, the constraints can be reformulated based on Equations~\eqref{linear-programming-problem} and~\eqref{software-communication-costs} as
